---
title: "week_07_notes"
author: "Abby Bergman"
date: "2/19/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(pwr)



```


```{r}
#t.test
#pwr.t.test(n=, d =, sig.level = , type = , alternative = )
#d = effsize, m1-m2/sd
# r assumes sig = .05
#type: default is ind samples
#alternative: whether the test is two sided (default: "two.sided"), (one sides: "less" or "greater")



```
Ex:
  Ha : no difference between drivers using cell phone and not
  Ho : mu1 - mu 2 = 1
  
  d = 1/1.25 = .8
  
```{r}
pwr.t.test(d = .8, sig.level = .05, power = .9)
```

Ex:
  d = .5
  n = 40
  sig level = .01
```{r}

pwr.t.test(d = .5, n = 20, sig.level = .01)

#less than 14% chance of declaring a difference of .625 seconds (d = mu1-mu2 / SD)
#d = .5 = ?/1.25 = .625

# if unequal sample size, use pwr.t2n.test(n1=, n2=, d=, sig.level= , alternative=)
```
ANOVA
format: pwr.anova.test(k= , n= , f= , sig.level= , power= )
  k: number of groups
  
Ex:
  k= 5
  power= .8
  f = .25
  sig.level = .05
```{r}
pwr.anova.test(k= 5, n= , f= .25, sig.level= .05, power= .8)


```
Correlation
  format: pwr.r.test(n= , r=, sig.level= , power= , alternative =)
  r= correlation coefficient
```{r}
pwr.r.test(r= .25, sig.level= .05, power= .9, alternative = "greater")

```


Linear Models
  format: pwr.f2.test(u= , v=, f2= , sig.level= , power= )
  u: the numberator (associated with model DF) 
  v: denominator (associated with error term DF)
  f2: effect size
  
  f21: used when youre evaluating a set of predictors on an outcome
  f22: used when youre evaluating a set of predictors above and beyond an original set of predictors
```{r}
pwr.f2.test(u=3, f2= .07692308, sig.level= .05, power= .9)

#u is total number of b preductors - 1
.05/(1-.35)

#n = 184 + 8 = 192
```